Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-10-30 02_Paper/paper.tex
Update corresponding author and keywords
Paper structure
Update structure

\aucores{* Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000. {\it E-mail address:} author@institute.xxx}

@@

\begin{keyword}
Type your keywords here, separated by semicolons ;

@@

\section{Introduction}

\section{Related Works}

\section{The Demo-Cell}

\section{Methods}

\section{Experiments}

\section{Conclusion}

>>>>

\aucores{* Corresponding author. Tel.: +49-271-740-4509; fax: +49-271-740-2630. {\it E-mail address:} alejandro.perez@uni-siegen.de}

@@

\begin{keyword}
Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Logistic Regression

@@

\section{Introduction} % 1 Page (incl authors, abstract)

% a)	Products’ quality must always be guaranteed.
% b)	In certain cases (especially in series assembly production) there is a delay between quality inspection and end of the production process  high potential for producing scrap 
% c)	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
% d)	Cost of quality check might be expensive
% e)	Quality assurance is normally done at the end of production (for assembly processes)   
% f)	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
% g)	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions  with the data collected from the machines, prediction models can be implemented for specific predicted values

\section{Related Works} % 1 Page

\subsection{Quality check in production} % Basic books (find summarize) basic concepts

% a)	How quality check is done in production
%        i)	Concepts and sampling plan
%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]

\subsection{Predictive analytics in production}

% b)	Predictive analytics in production focusing in QA
%        i)	Existing approaches and methods

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page

% What is the demozelle and why it is relevant as study case
% a)	Description of the assemble process in the Demozelle 
% Incl pictures

\section{Methods} %3/4 Page

% b)	Data  is collected from the demonstration cell and analyzed 
% c)	ML model [regression] is trained [type of model tbd]

\section{Experiments} % 1.5 Pages

\subsection{Lesson Learned} % 1/2 Page

% h)	Explain experiences by doing the research

\section{Conclusion} % 1/2 Page
